\LaTeX\ Author Guidelines for ICCV Proceedings

### 2019-05-20 chapters/3_algorithm.tex
Update formalism and minor changes

\TODO{Update inconsistent notation}We consider an undirected simple edge-weighted graph $\mathcal{G}(V,E,w^+, w^-)$ with both attractive and repulsive edge attributes. In computer vision applications, the nodes can represent either pixels, superpixels or voxels. We call the set $\Pi$ a \emph{clustering} or \emph{partitioning} with $K$ clusters if $V = \cup_{i=1}^K S_i $, $\,S_i \cap S_j = \emptyset$ for each $i\neq j$ and every $S \in \Pi$ induces a connected subgraph of $\mathcal{G}$. We also denote as $S_u$ the cluster associated with node $u$.
% \begin{equation}
% S_u \equiv S \in \Pi \,\, \text{s.t.} \,\, u \in S
% \end{equation}
% In this work, we consider the problem of clustering a weighted graph $\mathcal{G}(V,E,w^+, w^-)$ with both attractive and repulsive edge attributes. 
The weight function $w^+: E \rightarrow \mathbb{R}^+$ associates a positive scalar attribute $w_e^+\in \mathbb{R}^+$ representing a merge affinity or a similarity measure: the higher this number, the higher the inclination of the two incident vertices to be assigned to the same cluster\footnote{Note that other formalisms \UPDATE{REFS} for positively weighted graphs associate distances to the edges, thus, the \emph{lower} the edge weight, the higher the attraction between the two linked nodes, contrary to our definition of $w^+$.}. On the other hand, $w^-: E \rightarrow \mathbb{R}^+$ associates a split tendency $w_e^- \in \mathbb{R}^+$: the higher this weight, the more the incident vertices would like to be in different clusters. 
Graphs of the type $\mathcal{G}(V,E,w^+, w^-)$ are also often defined as \emph{signed graphs} $\mathcal{G}(V,E,\cost)$, featuring positive and negative edge weights $\cost_e\in \mathbb{R}$. Following the theoretical considerations in \cite{lange2018partial}, we define these signed weights as ${\cost_e = w_e^+ - w_e^-}$. Some approaches directly compute $\cost_e$, whereas others compute $w_e^+$ and $w_e^-$ separately.
In this formalism, graphs with purely attractive interactions are a special case of $\mathcal{G}(V,E,\cost)$ with $\cost_e \geq 0, \, \forall e \in E$.

\textbf{Inter-cluster interaction } We call two clusters $S_i,S_j$ \emph{adjacent} if there exists at least one edge ${e_{uv}\in E}$ connecting a node $u\in S_i$ to a node $v\in S_j$. In agglomerative HC, the interaction $\interact(S_i,S_j)$ between the two clusters is usually defined as a function, named \emph{linkage criterion}, depending on the weights of \emph{all} edges connecting clusters $S_i$ and $S_j$. 
All the linkage criteria tested in this article are listed and defined in Table \ref{tab:linkage-criteria}.
% For example, for a \emph{maximum} linkage criterion statistic (single-linkage), the inter-cluster interaction is given by:
% \begin{equation}\label{eq:max_linkage}
% \interact_{S_1,S_2} = \, \max_{e\in U(S_u,S_v)} \cost(e), \qquad \text{where}\quad E_{12} = \{ e_{uv} \in E | u \in S_1, \, v \in S_2 \}.
% \end{equation}
% Other common choices are \emph{minimum} (complete linkage) or \emph{average} (average linkage). %and \emph{sum}.

@@

In the special case of an unsigned graph with only positive interactions, i.e. $w_e^-=0$ and $\cost_e \geq 0$ $\forall e\in E$, %$\mathcal{G}(V,E,W:E\rightarrow \mathbb{R}^+)$ 
 the algorithm performs a standard agglomerative HC by returning only a single cluster and a hierarchy of clusters defined by the order in which the clusters are merged (see left panel of Fig. \hyperref[fig:intro_figure]{\ref*{fig:intro_figure}} and Table \ref{tab:linkage-criteria}, unsigned graphs).

>>>>

We consider an undirected simple edge-weighted graph $\mathcal{G}(V,E,w^+, w^-)$ with both attractive and repulsive edge attributes. In computer vision applications, the nodes can represent either pixels, superpixels or voxels. We call the set $\Pi$ a \emph{clustering} or \emph{partitioning} with $K$ clusters if $V = \cup_{S\in\Pi} S $, $\,S \cap \tilde{S} = \emptyset$ for different clusters $S, \tilde{S}\in \Pi$ and every cluster $S \in \Pi$ induces a connected subgraph of $\mathcal{G}$. We also denote as $S_u$ the cluster associated with node $u$.
% \begin{equation}
% S_u \equiv S \in \Pi \,\, \text{s.t.} \,\, u \in S
% \end{equation}
% In this work, we consider the problem of clustering a weighted graph $\mathcal{G}(V,E,w^+, w^-)$ with both attractive and repulsive edge attributes. 
The weight function $w^+: E \rightarrow \mathbb{R}^+$ associates to every edge a positive scalar attribute $w_e^+\in \mathbb{R}^+$ representing a merge affinity or a similarity measure: the higher this number, the higher the inclination of the two incident vertices to be assigned to the same cluster\footnote{Note that other formalisms \UPDATE{REFS} for positively weighted graphs associate distances to the edges, thus, the \emph{lower} the edge weight, the higher the attraction between the two linked nodes, contrary to our definition of $w^+$.}. On the other hand, $w^-: E \rightarrow \mathbb{R}^+$ associates to each edge a split tendency $w_e^- \in \mathbb{R}^+$: the higher this weight, the more the incident vertices would like to be in different clusters. 
Graphs of the type $\mathcal{G}(V,E,w^+, w^-)$ are also often defined as \emph{signed graphs} $\mathcal{G}(V,E,\cost)$, featuring positive and negative edge weights $\cost_e\in \mathbb{R}$. Following the theoretical considerations in \cite{lange2018partial}, we define these signed weights as ${\cost_e = w_e^+ - w_e^-}$. Some approaches directly compute $\cost_e$, whereas others compute $w_e^+$ and $w_e^-$ separately.
In this formalism, graphs with purely attractive interactions are a special case of $\mathcal{G}(V,E,\cost)$ with $\cost_e \geq 0, \, \forall e \in E$.

\textbf{Inter-cluster interaction } We call two clusters $S_u,S_v$ \emph{adjacent} if there exists at least one edge ${e_{ts}\in E}$ connecting a node $t\in S_u$ to a node $s\in S_v$. In hierarchical agglomerative clustering, the interaction $\interact(S_u,S_v)$ between the two clusters is usually defined as a function $\interact{}:\Pi \times \Pi \rightarrow \mathbb{R}$, named \emph{linkage criterion}, depending on the weights of \emph{all} edges connecting clusters $S_u$ and $S_v$, i.e. $E_{uv}=(S_u \times S_v) \cap E$. 
All the linkage criteria tested in this article are listed and defined in Table \ref{tab:linkage-criteria}.
% For example, for a \emph{maximum} linkage criterion statistic (single-linkage), the inter-cluster interaction is given by:
% \begin{equation}\label{eq:max_linkage}
% \interact_{S_1,S_2} = \, \max_{e\in U(S_u,S_v)} \cost(e), \qquad \text{where}\quad E_{12} = \{ e_{uv} \in E | u \in S_1, \, v \in S_2 \}.
% \end{equation}
% Other common choices are \emph{minimum} (complete linkage) or \emph{average} (average linkage). %and \emph{sum}.

@@

In the special case of an unsigned graph with only positive interactions, i.e. $w_e^-=0$ and $\cost_e \geq 0$ $\forall e\in E$, %$\mathcal{G}(V,E,W:E\rightarrow \mathbb{R}^+)$ 
 the algorithm performs a standard agglomerative hierarchical clustering by returning only a single cluster and a hierarchy of clusters defined by the order in which the clusters are merged (see left panel of Fig. \hyperref[fig:intro_figure]{\ref*{fig:intro_figure}} and Table \ref{tab:linkage-criteria}, unsigned graphs).

### 2019-05-20 chapters/supplementary.tex
Finish polishing intro, abstract, conclusions
Update figs and re-arrange
Update formalism and minor changes

\subsection{Properties of \algname{} with \emph{Absolute Maximum} linkage}
\paragraph{Remark on graph notation} The definition of a graph proposed by \cite{wolf2018mutex} makes a distinction between a set of positive edges $E^+$, associated with a set $W^+$ of positive scalar attributes representing merge affinities, and a set of negative edges $E^-$, associated with a set $W^-$ of positive attributes representing split tendencies. On the other hand, in our definition $\mathcal{G}(V,E,w^+,w^-)$ each edge have both an attractive $w_e^+$ and a repulsive $w_e^-$ attribute, so we can make them equivalent by defining:
\begin{align}
E^+ = \{ e \in E \,\,\text{s.t.} \,\,w_e = w_e^+ - w_e^- > 0\},& \qquad E^- = \{ e \in E \,\,\text{s.t.}\,\, w_e = w_e^+ - w_e^- \leq 0\} \\
W^+ = \{ |w_e| \,\,\text{s.t.}\,\, e \in E^+\},& \qquad W^- = \{ |w_e| \,\,\text{s.t.}\,\, e \in E^-\}
\end{align}

@@

\paragraph{Multi-step pipelines} Given the 2D WSDT superpixels, we build a 3D region-adjacency graph such that each node represents a superpixel. The weights of the edges connecting neighboring superpixels are computed by taking an average over both short- and long-range affinities connecting the two regions. We then convert the edge probabilities to signed weights using the logarithmic mapping defined in Eq. \ref{eq:mappings} and solve the multicut problem on this graph. For our experiments, we use the approximate Kernighan-Lin solver \cite{keuper2015efficient,kernighan1970efficient} (MC). In some cases, the long-range affinities predicted by the CNN can connect two superpixels that are not direct-neighbors. Thus, in these cases we introduce additional \emph{lifted} edges in the graph and an instance of the lifted multicut problem (LMC). This time, similarly to the methods mentioned in \cite{beier2016efficient}, we used a combination of approximate solvers consisting in GAEC and Kernighan-Lin. and      Other state-of-the-art multi-step-pipelines for neuron-segmentation first find 2D superpixels using WSDT and then apply a graph partitioning algorithm: in our comparison, we include one pipeline using agglomerative HC with average linkage (avgHC) and one using an approximation of the Lifted Multicut Problem (LMC) \cite{beier2016efficient}.

@@

 % In this section we evaluate the robustness of \algname{} with different linkage criteria by adding noise to the edge weights.
  %Before to present the results shown in Fig. \ref{fig:noise_plots}, we will first introduce the type of noise that was added to the edge weights.
% In our experiments, edge weights are estimated \UPDATE{by using a CNN that predicts how likely two neighboring pixels are to be part of the same cluster}. 
Fig. \hyperref[fig:noisy_affs]{\ref*{fig:noisy_affs}a} shows an example of uncertain CNN predictions on a part of the neuron segmentation CREMI dataset. We now present a way of modifying the CNN output to introduce additional artifacts like a missing or false boundary evidence.

>>>>

\subsection{Properties of \algname{} with \emph{Absolute Maximum} linkage}\label{sec:appendix_abs_max}
\paragraph{Remark on graph notation} The definition of a graph proposed by \cite{wolf2018mutex} makes a distinction between a set of positive edges $E^+$, associated with a set $W^+$ of positive scalar attributes representing merge affinities, and a set of negative edges $E^-$, associated with a set $W^-$ of positive attributes representing split tendencies. On the other hand, in our definition $\mathcal{G}(V,E,w^+,w^-)$ each edge have both an attractive $w_e^+$ and a repulsive $w_e^-$ attribute, so we can make them equivalent by defining:
\begin{align}
E^+ = \{ e \in E \,\,\text{s.t.} \,\,w_e = w_e^+ - w_e^- > 0\},& \qquad E^- = \{ e \in E \,\,\text{s.t.}\,\, w_e = w_e^+ - w_e^- \leq 0\} \\
W^+ = \{ |w_e| \,\,\text{s.t.}\,\, e \in E^+\},& \qquad W^- = \{ |w_e| \,\,\text{s.t.}\,\, e \in E^-\}
\end{align}

@@

\paragraph{Multi-step pipelines} Given the 2D WSDT superpixels, we build a 3D region-adjacency graph such that each node represents a superpixel. The weights of the edges connecting neighboring superpixels are computed by taking an average over both short- and long-range affinities connecting the two regions. We then convert the edge probabilities to signed weights using the logarithmic mapping defined in Eq. \ref{eq:mappings} and solve the multicut problem on this graph. For our experiments, we use the approximate Kernighan-Lin solver \cite{keuper2015efficient,kernighan1970efficient} (WSDT+MC). In some cases, the long-range affinities predicted by the CNN can connect two superpixels that are not direct-neighbors. Thus, in these cases we introduce additional \emph{lifted} edges in the graph and an instance of the lifted multicut problem (WSDT+LMC). This time, similarly to the methods mentioned in \cite{beier2016efficient}, we used a combination of approximate solvers consisting in GAEC and Kernighan-Lin. 
%and      Other state-of-the-art multi-step-pipelines for neuron-segmentation first find 2D superpixels using WSDT and then apply a graph partitioning algorithm: in our comparison, we include one pipeline using hierarchical agglomerative clustering with average linkage (avgHC) and one using an approximation of the Lifted Multicut Problem (LMC) \cite{beier2016efficient}.

@@

 % In this section we evaluate the robustness of \algname{} with different linkage criteria by adding noise to the edge weights.
  %Before to present the results shown in Fig. \ref{fig:noise_plots}, we will first introduce the type of noise that was added to the edge weights.
% In our experiments, edge weights are estimated \UPDATE{by using a CNN that predicts how likely two neighboring pixels are to be part of the same cluster}. 
A crop of CREMI training data sample B was used.

Fig. \hyperref[fig:noisy_affs]{\ref*{fig:noisy_affs}a} shows an example of uncertain CNN predictions on a part of the neuron segmentation CREMI dataset. We now present a way of modifying the CNN output to introduce additional artifacts like a missing or false boundary evidence.
